Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-27 paper.tex

%Short Research reviews should be in the range 3500–4000 words, with up to 40 references and 6 figures/tables.

@@

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods, has facilitated the comprehensive study of introgression across a broad spectrum of domesticated species (\textbf{Table 1}).
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on three broad categories of methods that explicitly identify introgressed genomic segments based on the extent of differentiation, patterns of nucleotide/haplotype sharing, and phylogenetic relationships.

@@

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=17.35cm]{temperature_plot.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature. The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=17.35cm]{./FigsAndTables/Figure1new}
	\caption{Hapmix vectors indicating introgression level from \emph{mexicana} to Mexican highland maize on chromosome 4. Data adopted from Hufford et al. \cite{Hufford2013}. ELP: EL Porvenir; IXT: Ixtlan ; NAB: Nabogame; OPO: Opopeo; PUR: Puruandiro; SAC: Santa Clara; SAP: San Pedro; TEN: Tenango del Aire; XOC: Xochimilco. Insets showed the phenotypes of macrohairs on lowland (red) and highland (blue) maize stems. The black bar indicated one of the QTLs for macrohairs and pigment density in Lauter et al. \cite{lauter2004}.}
	\label{fig:introgressionMaize}
\end{figure}

@@

\begin{table}[b]

\rowcolors{2}{white}{gray!25}
\begin{center}
\caption{List and brief description of recently developed methods and examples of empirical studies employing these methods.} \label{tab:tools}
\begin{tabularx}{\textwidth}{llll}
\\\toprule  
\rowcolor{white}
{\bf Methods}	& {\bf Data Type } &	{\bf References} &  {\bf Applications } \\ \midrule

\begin{table}
\centering
\begin{adjustbox}{width=1\textwidth}
\small
\label{my-label}
\begin{tabular}{|p{5cm}|p{5cm}|p{2.6cm}|p{2.6cm}|p{2.6cm}|l|}
\hline
Crop & Compatible Wild Relatives & Hybrids and/or Hybridization & Evidence of Crop Introgression & Evidence of Adaptiveness & Source \\ \hline \hline
Maize (\emph{Zea mays} subsp. \emph{mays}) & \emph{Z. m.} subsp. \emph{mexicana}, \emph{Z. m. } subsp. \emph{parviglumis} & X & X & X & \cite{Hufford2013} \\ 
\hline 
Asian Rice (\emph{Oryza sativa}) & \emph{O. rufipogon} & X & X & X & \cite{Huang2012} \\ 
\hline
Barley (\emph{Hordeum vulgare}) & \emph{H. v.} subsp. \emph{spontaneum} & X & X & X & \cite{Poets2015} \\ \hline
Sunflower (\emph{Helianthus annuus}) & \emph{H. argophyllus}, \emph{H. bolanderi}, \emph{H. debilis}, \emph{H. petiolaris} & X &   &   & \cite{rieseberg2007hybridization}\\ 
\hline
Cassava (\emph{Manihot esculenta}) & \emph{M. glaziovii} & X & X & X & \cite{bredeson2016sequencing} \\ 
\hline
Potato (\emph{Solanum tuberosum}) & many & X & X & X & \cite{hardigan2017genome, johns1986ongoing, gavrilenko2013genetic} \\
\hline
Tomato (\emph{Solanum lycopersicum}) & \emph{S. pimpinellifolium} & X & X & X & \cite{rick1958role} \\
\hline
Olive (\emph{Olea europaea} ssp. \emph{europaea} var. \emph{sativa}) & \emph{O. e.} ssp. \emph{europaea} var. \emph{sylvestris} & X & X & & \cite{diez2015olive} \\ 
\hline
Soybeans (\emph{Glycine max}) & \emph{G. soja} & X & X &  & \cite{lam2010resequencing} \\ 
\hline
Common Bean (\emph{Phaseolus vulgaris}) & \emph{P. v.} var. \emph{aborigineus, P. v.} var. \emph{mexicanus} [[not in this source]]& X & X &  & \cite{papa2003asymmetry} \\
\hline
Grapes (\emph{Vitis vinifera} subsp. \emph{vinifera}) & \emph{V. v.} subsp. \emph{sylvestris} & X & X &  &  \cite{myles2011genetic} \\
\hline
Sorghum (\emph{Sorghum bicolor} subsp. \emph{bicolor}) & \emph{S. b.} subsp. \emph{arundinaceum, S. b.} subsp. {drummondii} & X & X &  & \cite{aldrich1992patterns} \\
\hline
Wheat (\emph{Tritium monococcum, T. dicoccum, T. aestivum}) & \emph{T. m. boeoticum, T. dioccoides, T. urartu, Aegilops speltoides, A. tauschii} & X & X &  & \cite{zohary1969wild} \\
\hline
Apple (\emph{Malus domesticus}) & \emph{M. sylvestris}, \emph{M. orientalis}, \emph{M. baccata}, \emph{M. sieversii}  & X & X & & \cite{cornille2012new} \\
\hline
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

@@

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods (\textbf{Table 1}), has facilitated the comprehensive study of introgression across a broad spectrum of domesticated species.
The methods reviewed here do not include those marginally estimating introgression\slash migration rate as a component of demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and a series of methods utilizing the sequentially Markovian coalescent (PSMC, MSMC and SMC++) \cite{li2011, schiffels2014, terhorst2017}). 
Rather, we focus on three broad categories of methods that explicitly identify introgressed genomic segments based on the extent of differentiation, patterns of nucleotide/haplotype sharing, and phylogenetic relationships.

@@

\begin{table}[h]

\rowcolors{2}{white}{gray!25}
\begin{center}
\caption{List of recently developed methods for detecting introgression and examples of their use in empirical studies.} \label{tab:tools}
\begin{tabularx}{\textwidth}{llll}
\\\toprule  
\rowcolor{white}
{\bf Methods}	& {\bf Data Type } &	{\bf References} &  {\bf Applications } \\ \midrule

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=15cm]{temperature_plot.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature. Approximate domestication center for each crop is denoted by a triangle}
	\label{fig:map}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=12cm]{./FigsAndTables/Figure1new}
	\caption{Hapmix vectors indicating introgression level from \emph{mexicana} to Mexican highland maize on chromosome 4. Data adopted from Hufford et al. \cite{Hufford2013}. ELP: EL Porvenir; IXT: Ixtlan ; NAB: Nabogame; OPO: Opopeo; PUR: Puruandiro; SAC: Santa Clara; SAP: San Pedro; TEN: Tenango del Aire; XOC: Xochimilco. Insets show the phenotypic differences between lowland (red) and highland (blue) maize stems. The black bar indicates one of the QTLs for macrohairs and pigment density in Lauter et al. \cite{lauter2004}.}
	\label{fig:introgressionMaize}
\end{figure}

@@

%\centering
%\begin{adjustbox}{width=1\textwidth}
%\small
%\label{my-label}
%\begin{tabular}{|p{5cm}|p{5cm}|p{2.6cm}|p{2.6cm}|p{2.6cm}|l|}
%\hline
%Crop & Compatible Wild Relatives & Hybrids and/or Hybridization & Evidence of Crop Introgression & Evidence of Adaptiveness & Source \\ \hline \hline
%Maize (\emph{Zea mays} subsp. \emph{mays}) & \emph{Z. m.} subsp. \emph{mexicana}, \emph{Z. m. } subsp. \emph{parviglumis} & X & X & X & \cite{Hufford2013} \\ 
%\hline 
%Asian Rice (\emph{Oryza sativa}) & \emph{O. rufipogon} & X & X & X & \cite{Huang2012} \\ 
%\hline
%Barley (\emph{Hordeum vulgare}) & \emph{H. v.} subsp. \emph{spontaneum} & X & X & X & \cite{Poets2015} \\ \hline
%Sunflower (\emph{Helianthus annuus}) & \emph{H. argophyllus}, \emph{H. bolanderi}, \emph{H. debilis}, \emph{H. petiolaris} & X &   &   & \cite{rieseberg2007hybridization}\\ 
%\hline
%Cassava (\emph{Manihot esculenta}) & \emph{M. glaziovii} & X & X & X & \cite{bredeson2016sequencing} \\ 
%\hline
%Potato (\emph{Solanum tuberosum}) & many & X & X & X & \cite{hardigan2017genome, johns1986ongoing, gavrilenko2013genetic} \\
%\hline
%Tomato (\emph{Solanum lycopersicum}) & \emph{S. pimpinellifolium} & X & X & X & \cite{rick1958role} \\
%\hline
%Olive (\emph{Olea europaea} ssp. \emph{europaea} var. \emph{sativa}) & \emph{O. e.} ssp. \emph{europaea} var. \emph{sylvestris} & X & X & & \cite{diez2015olive} \\ 
%\hline
%Soybeans (\emph{Glycine max}) & \emph{G. soja} & X & X &  & \cite{lam2010resequencing} \\ 
%\hline
%Common Bean (\emph{Phaseolus vulgaris}) & \emph{P. v.} var. \emph{aborigineus, P. v.} var. \emph{mexicanus} [[not in this source]]& X & X &  & \cite{papa2003asymmetry} \\
%\hline
%Grapes (\emph{Vitis vinifera} subsp. \emph{vinifera}) & \emph{V. v.} subsp. \emph{sylvestris} & X & X &  &  \cite{myles2011genetic} \\
%\hline
%Sorghum (\emph{Sorghum bicolor} subsp. \emph{bicolor}) & \emph{S. b.} subsp. \emph{arundinaceum, S. b.} subsp. {drummondii} & X & X &  & \cite{aldrich1992patterns} \\
%\hline
%Wheat (\emph{Tritium monococcum, T. dicoccum, T. aestivum}) & \emph{T. m. boeoticum, T. dioccoides, T. urartu, Aegilops speltoides, A. tauschii} & X & X &  & \cite{zohary1969wild} \\
%\hline
%Apple (\emph{Malus domesticus}) & \emph{M. sylvestris}, \emph{M. orientalis}, \emph{M. baccata}, \emph{M. sieversii}  & X & X & & \cite{cornille2012new} \\
%\hline
%\end{tabular}
%\end{adjustbox}
%\end{table}
